Deep learning for geophysics

### 2023-10-11 manuscript.tex
Fix long bibliography, use pdf 1.6
Add short headings to suit ToC
Tweak headings, refs

\documentclass[12pt,a4paper]{report} %,openright,twoside
% \includeonly{}
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}
\begin{document}

\begin{titlepage}
    \centering

@@

\addsec{\centering{}Abstract}
Geophysics examines the petrophysical expression of geology within the Earth and is vital for exploring and understanding mineral systems under cover.
The growing global demand for resources drives new data acquisition, with sensors that return more and higher quality data.
The challenges and opportunities of big data are not unique to the geosciences, and the development of methods and computing to address these are ubiquitous in the contemporary age of deep learning.

@@

\newpage{}
\tableofcontents{}
\listoffigures{}
% \listoftables{}

\newpage{}
\addsec{Thesis Declaration}
I, Luke Thomas Smith, certify that:
\begin{itemize}
    \item{}This thesis has been substantially accomplished during enrolment in this degree.
    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
\end{itemize}

@@

\newpage{}
% \subfile{authorship_declaration}
% Fix incorrect page numbering
\includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}

@@

\chapter{Introduction}
\label{ch:intro}
% \subfile{intro}
% \includepdf[pages=-]{intro.pdf}
\include{intro}

\chapter{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{ch:paper1}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

Smith, L., Horrocks, T., Holden, E.-J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119.
https://doi.org/10.1016/j.oregeorev.2022.105119
% \subfile{paper1}
% \includepdf[pages=-]{paper1.pdf}
\include{paper1}

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{ch:paper2}
% \includepdf[pages=-]{paper2.pdf}
% \subfile{paper2}
\include{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{ch:paper3}
% \includepdf[pages=-]{paper3.pdf}
% \subfile{paper3}
\include{paper3}

% \includepdf[pages=-]{discussion.pdf}
% \subfile{discussion}
\include{discussion}

>>>>

\directlua{pdf.setminorversion(6)}
\documentclass[12pt,a4paper,notitlepage]{report} %,openright,twoside scrbook
% \includeonly{}
\usepackage{thesisstyle}
\addbibresource{bib/PhD.bib}
\begin{document}

\pagenumbering{Alph}
\begin{titlepage}
    \centering

@@

\addsec[Abstract]{\centering Abstract}
Geophysics examines the petrophysical expression of geology within the Earth and is vital for exploring and understanding mineral systems under cover.
The growing global demand for resources drives new data acquisition, with sensors that return more and higher quality data.
The challenges and opportunities of big data are not unique to the geosciences, and the development of methods and computing to address these are ubiquitous in the contemporary age of deep learning.

@@

\newpage{}
\tableofcontents{}
\listoffigures{}

\newpage{}
\addsec[Declarations]{Thesis Declaration}
I, Luke Thomas Smith, certify that:
\begin{itemize}
    \item{}This thesis has been substantially accomplished during enrolment in this degree.
    \item{}This thesis is my own work and does not contain any material previously published or written by another person, except where due reference has been made in the text or Authorship Declaration.
    \item{}This thesis does not contain material which has been submitted for the award of any other degree or diploma in my name, in any university or other tertiary institution.
    \item{}In the future, no part of this thesis will be used in a submission in my name, for any other degree or diploma in any university or other tertiary institution without the prior approval of The University of Western Australia and where applicable, any partner institution responsible for the joint-award of this degree.
    \item{}This thesis does not violate or infringe any copyright, trademark, patent, or other rights whatsoever of any person.
\end{itemize}

@@

\newpage{}
% Fix incorrect page numbering
\includepdf[pages=-,templatesize={595.276pt}{841.89pt},nup=1x1,scale=1,clip,trim=5mm 36.5mm 5mm 20mm,fitpaper=true,pagecommand={\pagestyle{plain}}]{authorship_declaration_signed.pdf}

@@

\chapter{Introduction}
\label{ch:intro}
\newrefsection{}
\include{intro}

\chapter[Magnetic Grid Resolution Enhancement using ML]{Magnetic Grid Resolution Enhancement using Machine Learning}
\label{ch:paper1}
\newrefsection{}
This chapter has been reproduced from the following peer reviewed publication. Formatting has been adjusted for consistency.

Smith, L., Horrocks, T., Holden, E.-J., Wedge, D., Akhtar, N., 2022. Magnetic grid resolution enhancement using machine learning: A case study from the Eastern Goldfields Superterrane. Ore Geology Reviews 150, 105119.
https://doi.org/10.1016/j.oregeorev.2022.105119
\include{paper1}

\chapter{Super-resolution of Aeromagnetic Survey Data}
\label{ch:paper2}
\newrefsection{}
\include{paper2}

\chapter{Implicit Neural Representation for Potential Field Geophysics}
\label{ch:paper3}
\newrefsection{}
\include{paper3}

\newrefsection{}
\include{discussion}
